### 2020-05-12 papers-vol-3.tex
Split into three volumes

% TODO
% [ ] move each commentary directly after each long paper
% [ ] fill in titles of commentaries
% [ ] fill in full author for each commentary
% [ ] Latexify all the weird unicode names (https://en.wikibooks.org/wiki/LaTeX/Special_Characters)

\part{Long papers}

\insertmydocument{chapter}{Argumentative Design and Polylogue}{Mark Aakhus}{pdfs/long/1longAakhus.docx.pdf}
\insertmydocument{chapter}{What is Wrong with Deductivism?}{Lilian Bermejo-Luque}{pdfs/long/3LongBermejo-Luque.doc.pdf}

\insertmydocument{chapter}{Is There an Informal Logic Approach to Argument?}{J. Anthony Blair}{pdfs/long/4longBlair.docx.pdf}
\insertmydocument{chapter}{Commentary on Blair’s Is there an informal logic approach to argument?}{Paula Olmos}{pdfs/commentary/4longBlair-C.doc.pdf}

\insertmydocument{chapter}{Structural Differences Between Practical and Cognitive Presumptions}{Petar Bodlovi\'{c}}{pdfs/long/5longBodlovic.doc.pdf}
\insertmydocument{chapter}{Commentary on Bodlovi\'{c} Structural Differences Between Practical and Cognitive Presumptions}{James B. Freeman}{pdfs/commentary/5longBodlovic-C.doc.pdf}

\insertmydocument{chapter}{Reliability of Argument Mapping}{Sebastian Cacean}{pdfs/long/6longCacean.docx.pdf}
\insertmydocument{chapter}{Commentary on Cacean’s Reliability of Argument Mapping}{Roosmaryn Pilgram}{pdfs/commentary/6longCacean-C.doc.pdf}

\insertmydocument{chapter}{Critical discussion for sub-optimal settings}{Diego Castro}{pdfs/long/7longCastro.doc.pdf}
\insertmydocument{chapter}{Comments on Diego Castro’s Critical Discussion in Sub-Optimal Settings}{David Godden}{pdfs/commentary/7longCastro-C.doc.pdf}

\insertmydocument{chapter}{Democratic Legitimacy and Acts of Dissent}{Cristina Corredor}{pdfs/long/8longCorredor.docx.pdf}
\insertmydocument{chapter}{Dissent and Democracy -- Commentary on Corredor’s Democratic Legitimacy and Acts of Dissent}{David Zarefsky}{pdfs/commentary/8longCorredor-C.doc.pdf}

\insertmydocument{chapter}{Strength of Reasons for Moral Dissent}{James Freeman}{pdfs/long/9longFreeman.doc.pdf}
\insertmydocument{chapter}{What is Peculiar about Moral Dissent? Commentary on Freeman’s Strength of Reasons for Moral Dissent}{John Patrick Casey}{pdfs/commentary/9longFreeman-C.docx.pdf}

\insertmydocument{chapter}{Where Are Dissent and Reasons in Epistemic Justification?}{Jos\'{e} \'{A}ngel Gasc\'{o}n}{pdfs/long/10longGascon.doc.pdf}
\insertmydocument{chapter}{Knowledge and the Epistemic Function of Argumentation -- Commentary on Gasc\'{o}n's Where Are dissent and Reasons in Epistemic Justification?}{Christoph Lumer}{pdfs/commentary/10longGascon-C.doc.pdf}

\insertmydocument{chapter}{Justifying Questions?}{G.C. Goddu}{pdfs/long/11LongGoddu.doc.pdf}
\insertmydocument{chapter}{Commentary on G. C. Goddu’s Justifying Questions?}{David Hitchcock}{pdfs/commentary/11longGoddu-C.docx.pdf}

\insertmydocument{chapter}{Ethnography of Argumentation}{Kati Hannken-Illjes}{pdfs/long/12longHannkenilljes.docx.pdf}

\insertmydocument{chapter}{“’I said what I said’ - Black Women and Argumentative Politeness Norms”}{Tempest M Henning}{pdfs/long/13longHenning.docx.pdf}
\insertmydocument{chapter}{Commentary on Tempest Henning’s “’I Said What I Said’ - Black Women and Argumentative Politeness Norms”}{Catherine Hundleby}{pdfs/commentary/13longHenning-C.doc.pdf}

\insertmydocument{chapter}{The Argument Assessment Tutor (AAT)}{Michael H.G. Hoffmann}{pdfs/long/14longHoffmann.doc.pdf}

\insertmydocument{chapter}{Grice, Machine Head and the Problem of Overexpressed Premises}{Michael J. Hoppmann}{pdfs/long/15longHoppmann.doc.pdf}
\insertmydocument{chapter}{Commentary on Hoppmann’s Grice, Machine Head and the Problem of Overexpressed Premises}{Thierry Herman}{pdfs/commentary/15longHoppmann-C.docx.pdf}

\insertmydocument{chapter}{Standpoints and Commitments as Products of Argumentative Work: Micro/Macro- Analysis of an Infamous Press Conference}{Sally Jackson, Scott Jacobs, Xiaoqi Zhang}{pdfs/long/16longJackson.doc.pdf}
\insertmydocument{chapter}{A wanting analysis -- Commentary on S. Jackson, S. Jacobs, Y. Zhang's Standpoints and Commitments as Products of Argumentative Work: Micro/Macro-Analysis of an Infamous Press Conference}{Harald R. Wohlrapp}{pdfs/commentary/16longJackson-C.doc.pdf}

\insertmydocument{chapter}{Speech Act Pluralism in Argumentative Polylogues}{Marcin Lewi\'{n}ski}{pdfs/long/18longLewinski.doc.pdf}

\insertmydocument{chapter}{Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{John Licato, Michael Cooper}{pdfs/long/19longLicato.doc.pdf}
\insertmydocument{chapter}{Commentary on Licato {\&} Cooper's Evaluating Relevance in Analogical Arguments Through Warrant-based Reasoning}{Nicole Cruz}{pdfs/commentary/19longLicato-C.docx.pdf}

\insertmydocument{chapter}{Arguments From Expert Opinion – An Epistemological Approach}{Christoph Lumer}{pdfs/long/20longLumer.doc.pdf}

\insertmydocument{chapter}{All-out Attack}{Tshepo Bogosi Mosaka}{pdfs/long/21longMosaka.doc.pdf}

\insertmydocument{chapter}{Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Menno H. Reijven}{pdfs/long/22longReijven.doc.pdf}
\insertmydocument{chapter}{Commentary on Reijven’s Strategic Maneuvering with Speech Codes: The Rhetorical Use of Cultural Presumptions in Constructing Argumentative Discourse}{Beth Innocenti}{pdfs/commentary/22longReijven-C.doc.pdf}

\insertmydocument{chapter}{Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Karim Sadek}{pdfs/long/23longSadek.doc.pdf}
\insertmydocument{chapter}{Commentary on Sadek’s Disagreement, Public Reasoning, and (Non-)Authoritarian Argumentation}{Cristina Corredor}{pdfs/commentary/23longSadek-C.doc.pdf}

\insertmydocument{chapter}{Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate About Funding Prep}{Sean Sinclair}{pdfs/long/24longSinclair.doc.pdf}
\insertmydocument{chapter}{Commentary on Sinclair’s Uncovering Hidden Premises to Reveal the Arguer's Implicit Values: Analysing the Public Debate about Funding Prep}{Sally Jackson}{pdfs/commentary/24longSinclair-C.doc.pdf}

\insertmydocument{chapter}{Strange Fish: Belief and the Roots of Disagreement}{Christopher W. Tindale}{pdfs/long/25longTindale.docx.pdf}
\insertmydocument{chapter}{An optimistic perspective on deep disagreement? Commentary on Tindale’s Strange Fish: Belief and the Roots of Disagreement}{L\'{e}a Farine}{pdfs/commentary/25longTindale-C.doc.pdf}

\insertmydocument{chapter}{Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{G\'{a}bor \'{A} Zempl\'{e}n}{pdfs/long/27longZemplen.doc.pdf}
\insertmydocument{chapter}{Commentary on Zempl\'{e}n’s Profiling Dialogues: Multi-trait Mapping of Televised Argumentative Exchanges}{Mehmet Ali \"{U}zelg\"{u}n}{pdfs/commentary/27longZemplen-C.doc.pdf}

\part{Thematic papers}

\insertmydocument{chapter}{Visual and Auditory Schemes of Argument}{Leo Groarke}{pdfs/thematic/1regularthematicGroarke.docx.pdf}
\insertmydocument{chapter}{The Prospects for Multimodal Schemes of Argument: Assessing Adbusters’ Spoofing Strategies}{Assimakis Tseronis}{pdfs/thematic/3regularThematicTseronis.docx.pdf}
\insertmydocument{chapter}{(Mis)Framing Photographs as an Obstacle to Fair Dissent}{Marta Zampa, Chiara Pollaroli}{pdfs/thematic/4regularThematicZampa.docx.pdf}
\insertmydocument{chapter}{Dissent, Disadvantage, Testimony and the Ideological ‘Truth’ of Presumptions}{Harmony Peach}{pdfs/thematic/5regularThematicPeach.doc.pdf}
\insertmydocument{chapter}{With All Due Respect: Controversial Beliefs and the Limits of Responsible Argumentation}{Tracy Bowell}{pdfs/thematic/7regularThematicBowell.doc.pdf}
\insertmydocument{chapter}{A Quantitative Corpus-Based Study of Evidentiality and Disagreement in Earnings Conference Calls}{Andrea Rocci, Carlo Raimondo, Daniele Puccinelli}{pdfs/thematic/9regularThematicRocci.docx.pdf}
\insertmydocument{chapter}{Five Approaches to Argument Strength: Probabilistic, Dialectical, Structural, Empirical, and Computational}{Frank Zenker, David Godden, Marcin Selinger, Simon Wells, Kamila Debowska-Kozlowska}{pdfs/thematic/13regularThematicZenkeretal.docx.pdf}
\insertmydocument{chapter}{Responsible Agent Deliberation}{Douglas Walton, Alice Toniolo}{pdfs/thematic/18regularThematicWalton.doc.pdf}
\insertmydocument{chapter}{From Dialogic to Argument-based Teaching: Significant Teacher Moves in Framing Classroom-based Argumentation Dialogues}{Chrysi Rapanta, Dilar Cascalheira}{pdfs/thematic/20regularThematicRapanta.doc.pdf}

% \addtocontents{toc}{\protect\newpage}
\part{Regular papers}

\insertmydocument{chapter}{What Optimistic Responses to Deep Disagreement get Right}{Scott F. Aikin}{pdfs/regular/2regularAikin.doc.pdf} % 2
\insertmydocument{chapter}{Is There a Crisis of Dissent and Disagreement in Argument Theory?}{Mark Alfino}{pdfs/regular/3regularAlfino.docx.pdf} % 3
\insertmydocument{chapter}{Epistemic Tolerance}{Dominik Balg}{pdfs/regular/7regularBalg.doc.pdf} % 7
\insertmydocument{chapter}{Structuring Controversy: The Dialectic of Disagreement}{Sharon Bailin, Mark Battersby}{pdfs/regular/8regularBailin.docx.pdf} % 8
\insertmydocument{chapter}{The Role of Reasoning and Arguing in Youth Democratic Participation in Canada}{Michael D. Baumtrog}{pdfs/regular/9regularBaumtrog.doc.pdf} % 9
\insertmydocument{chapter}{Pictures and Reasoning: Visual Arguments and Objections}{Angelina Bobrova}{pdfs/regular/11regularBobrova.docx.pdf} % 11
\insertmydocument{chapter}{Issues Leading to Argumentative Discussions During Family Mealtime Conversations}{Antonio Bova}{pdfs/regular/12regularBova.doc.pdf} % 12
\insertmydocument{chapter}{Value-based Argumentation and the Transition to Low Carbon Economy in Turkey and Portugal: Values, Uncertainty and Actions}{Huthaifah Busuulwa}{pdfs/regular/16regularBusuulwa.doc.pdf} % 16
\insertmydocument{chapter}{Dissent: Considering Culture and Personality}{Linda Carozza}{pdfs/regular/17regularCarozza.doc.pdf} % 17
\insertmydocument{chapter}{Heroic Argumentation: On Heroes, Heroism, and Glory in Arguments}{John Casey, Daniel Cohen}{pdfs/regular/18regularCasey.doc.pdf} % 18
\insertmydocument{chapter}{Relationships between Narrative and Argumentation. In Defence of a Functional Account}{Guillermo Sierra Catal\'{a}n}{pdfs/regular/19regularSierraCatalan.docx.pdf} % 19
\insertmydocument{chapter}{Interactive Discourse Features Supporting Aversive and Existential Acknowledgment In Legislative and Ceremonial Government Apologies}{Martha S. Cheng}{pdfs/regular/20regularCheng.docx.pdf} % 20
\insertmydocument{chapter}{Devil’s Advocates are the Angels of Argumentation}{Katharina Stevens, Daniel Cohen}{pdfs/regular/21regularCohen.docx.pdf} % 21
\insertmydocument{chapter}{The Semantic Mechanisms Underlying Disagreement. An Argumentative Semantics Approach}{Ana-Maria Cozma}{pdfs/regular/23regularCozma.docx.pdf} % 23
\insertmydocument{chapter}{Strategic Maneuvering in Implicit an Pseudo-explicit Advertising Discussion}{H\'{e}di Vir\'{a}g Csord\'{a}s}{pdfs/regular/25regularCSORDAS.doc.pdf} % 25
\insertmydocument{chapter}{Reasons for Rational Disagreement from Dialectics The Van Inwagen Cases}{Istvan Danka}{pdfs/regular/26regularDanka.doc.pdf} % 26
\insertmydocument{chapter}{Arguing Brexit on Twitter: A Corpus Linguistic Study}{Natalie Dykes, Philipp Heinrich, Stefan Evert}{pdfs/regular/28regularDykes.docx.pdf} % 28
\insertmydocument{chapter}{Protagoras’ Principles, Disagreement and the Possibility of Error}{Michel Dufour}{pdfs/regular/29regularDufour.doc.pdf} % 29
\insertmydocument{chapter}{Changing Minds through Argumentation: Black Pete as a Case Study}{Catarina Dutilh Novaes, Emily Sullivan, Thirza Lagewaard, Mark Alfano}{pdfs/regular/30regularDutilhNovaes.doc.pdf} % 30
\insertmydocument{chapter}{The Pragma-dialectical View of Comparison Argumentation}{Frans van Eemeren, Bart Garssen}{pdfs/regular/31regularEemeren.doc.pdf} % 31
\insertmydocument{chapter}{An Indexical Characterization of Disagreement Based on Possible Worlds Semantics}{L\'{e}a Farine}{pdfs/regular/35regularFarine.doc.pdf} % 35
\insertmydocument{chapter}{The Visual Rhetoric of Iconic Photographs as Topoi in Editorial Cartoons: an Argumentative Analysis}{Eveline Feteris}{pdfs/regular/36regularFeteris.doc.pdf} % 36
\insertmydocument{chapter}{Conceptual Analysis of an Argumentation using Argumentation Schemes and the Toulmin Model}{Marie Garnier, Patrick Saint-Dizier}{pdfs/regular/37regularGarnier.docx.pdf} % 37
\insertmydocument{chapter}{Representing Second-order Arguments with Adpositional Argumentation}{Federico Gobbo, Jean H.M. Wagemans}{pdfs/regular/39regularGobbo.doc.pdf} % 39
\insertmydocument{chapter}{Argumentation, Dissent, and Luck}{Job de Grefte}{pdfs/regular/44regularDeGrefte.doc.pdf} % 44
\insertmydocument{chapter}{Argument Scheme Theory}{Hans V Hansen}{pdfs/regular/45regularHansen.docx.pdf} % 45
\insertmydocument{chapter}{Resolution of Deep Disagreement: Not Simply Consensus}{Leah Henderson}{pdfs/regular/47regularHenderson.docx.pdf} % 47
\insertmydocument{chapter}{Appeals to Popularity: Roles and Functions of ‘Everyone knows X’}{Thierry Herman}{pdfs/regular/48regularHerman.docx.pdf} % 48
\insertmydocument{chapter}{Towards a Theory of Informal Argument Semantics}{Martin Hinton}{pdfs/regular/49regularHinton.doc.pdf} % 49
\insertmydocument{chapter}{Stereotyping}{David Hitchcock}{pdfs/regular/50regularHitchcock.doc.pdf} % 50
\insertmydocument{chapter}{Changing Norms of Argumentation}{Beth Innocenti}{pdfs/regular/53regularInnocenti.doc.pdf} % 53
\insertmydocument{chapter}{"If You Are A Scientist You Cannot Stop Such A Thing": Scientific Assent and Dissent in the Manhattan Project}{David Erland Isaksen}{pdfs/regular/54regularIsaksen.doc.pdf} % 54
\insertmydocument{chapter}{Formal Specifications for Dialogue Games in Multi-party Healthcare Coaching}{Mathilde Janier, Alison Pease, Mark Snaith, Dominic de Franco}{pdfs/regular/55regularJanier.docx.pdf} % 55
\insertmydocument{chapter}{How Courts Should Respond to the Stories Defendants Tell: A Bayesian Account of a Dutch Ruling}{Hylke Jellema}{pdfs/regular/57regularJellema.doc.pdf} % 57

@@

\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico Ezequiel L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

>>>>

\part{Regular papers}

@@

\insertmydocument{chapter}{Strategic Manoeuvring with the Construction “We (All) Know that X” in Parliamentary Debates}{Matthijs Looij, Bertijn van der Steenhoven}{pdfs/regular/74regularLooij.docx.pdf} % 74
\insertmydocument{chapter}{Argument, Justification and Inquiry: a Pragmatist Approach}{Federico E. L\'{o}pez}{pdfs/regular/75regularLopez.doc.pdf} % 75

### 2020-05-12 preface.tex
Split into three volumes

After two successful editions held in Lisbon in 2015 and Fribourg in 2017, ECA was hosted in 2019 by the Faculty of Philosophy of the University of Groningen, on 24-27 June 2019. These two volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.

The European Conference on Argumentation (ECA) is a pan-European biennial initiative aiming to consolidate and advance various strands of research on argumentation and reasoning by gathering scholars from a range of disciplines. While based in Europe, ECA involves and encourages participation by argumentation scholars from all over the world; it welcomes submissions linked to argumentation studies in general, in addition to those tackling the conference theme. The 2019 Groningen edition focused on dissent. The goal was to inquire into the virtues and vices of dissent, criticism, disagreement, objections, and controversy in light of legitimizing policy decisions, justifying beliefs, proving theorems, defending standpoints, or strengthening informed consent. It is well known that dissent may hinder the cooperation and reciprocity required for reason-based deliberation and decision-making. But then again, dissent also produces the kind of scrutiny and criticism required for reliable and robust outcomes. How much dissent does an argumentative practice require? What kinds of dissent should we promote, or discourage? How to deal with dissent virtuously? How to exploit dissent in artificial arguers? How has dissent been conceptualized in the history of rhetoric, dialectic and logic? The papers in these two volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).

The conference had 224 participants, and 188 papers were presented. These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation. The contents of these two volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.

@@

Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings. First of all, we must thank all members of our Scientific Panel and of our Programme Committee, thanks to whom we were able to select papers of the highest quality. In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants. Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these two volumes, and assisted us throughout in the process of producing the Proceedings.

>>>>

After two successful editions held in Lisbon in 2015 and Fribourg in 2017, ECA was hosted in 2019 by the Faculty of Philosophy of the University of Groningen, on 24-27 June 2019. These three volumes contain the Proceedings of this third edition of the conference series, whose special theme was Reason to Dissent.

The European Conference on Argumentation (ECA) is a pan-European biennial initiative aiming to consolidate and advance various strands of research on argumentation and reasoning by gathering scholars from a range of disciplines. While based in Europe, ECA involves and encourages participation by argumentation scholars from all over the world; it welcomes submissions linked to argumentation studies in general, in addition to those tackling the conference theme. The 2019 Groningen edition focused on dissent. The goal was to inquire into the virtues and vices of dissent, criticism, disagreement, objections, and controversy in light of legitimizing policy decisions, justifying beliefs, proving theorems, defending standpoints, or strengthening informed consent. It is well known that dissent may hinder the cooperation and reciprocity required for reason-based deliberation and decision-making. But then again, dissent also produces the kind of scrutiny and criticism required for reliable and robust outcomes. How much dissent does an argumentative practice require? What kinds of dissent should we promote, or discourage? How to deal with dissent virtuously? How to exploit dissent in artificial arguers? How has dissent been conceptualized in the history of rhetoric, dialectic and logic? The papers in these three volumes discuss these and other questions pertaining to argumentation and dissent (among other themes).

The conference had 224 participants, and 188 papers were presented. These high numbers are a clear indication that ECA continues to fulfill its role as a key platform of scholarly exchange in the field of argumentation. The contents of these three volumes can be regarded as a reflection of the current state of the art in argumentation scholarship in general.

@@

Many people have contributed to the success of ECA 2019, and for the completion of the Proceedings. First of all, we must thank all members of our Scientific Panel and of our Programme Committee, thanks to whom we were able to select papers of the highest quality. In Groningen, thanks to those who provided organizational support, in particular the team of student assistants (especially Johan Rodenburg) who ensured that the conference was a pleasant experience to all participants. Our heartfelt thanks go to Jelmer van der Linde and Annet Onnes, who accomplished the gigantic task of putting all the papers together into these three volumes, and assisted us throughout in the process of producing the Proceedings.
